 extracting environmenal and oceanographic variables

### 2024-01-24 03_environ_var.Rmd
Update 03_environ_var.Rmd

Save final df 'GPSwhaleAISenv' to add soundscape metrics next.
```{r}
saveRDS(env10, 'data/GPSwhaleAISenv10.rda')
saveRDS(env12, 'data/GPSwhaleAISenv12.rda')
saveRDS(env13, 'data/GPSwhaleAISenv13.rda')
saveRDS(env14, 'data/GPSwhaleAISenv14.rda')
saveRDS(env16, 'data/GPSwhaleAISenv16.rda')
saveRDS(env18, 'data/GPSwhaleAISenv18.rda')
saveRDS(env19, 'data/GPSwhaleAISenv19.rda')
saveRDS(env20, 'data/GPSwhaleAISenv20.rda')
saveRDS(env21, 'data/GPSwhaleAISenv21.rda')
saveRDS(env22, 'data/GPSwhaleAISenv22.rda')
saveRDS(env23, 'data/GPSwhaleAISenv23.rda')
saveRDS(env07, 'data/GPSwhaleAISenv07.rda')
saveRDS(env08, 'data/GPSwhaleAISenv08.rda')

>>>>

Save final df 'GPSwhaleAISenv' to add soundscape metrics next.
```{r}
# Remove points where buoy is on the shelf - 300 meters
#Only occurs with buoy 7
env07 <- env07 %>%
  filter(depth > 300)

saveRDS(env10, 'data/GPSwhaleAISenv10.rda')
saveRDS(env12, 'data/GPSwhaleAISenv12.rda')
saveRDS(env13, 'data/GPSwhaleAISenv13.rda')
saveRDS(env14, 'data/GPSwhaleAISenv14.rda')
saveRDS(env16, 'data/GPSwhaleAISenv16.rda')
saveRDS(env18, 'data/GPSwhaleAISenv18.rda')
saveRDS(env19, 'data/GPSwhaleAISenv19.rda')
saveRDS(env20, 'data/GPSwhaleAISenv20.rda')
saveRDS(env21, 'data/GPSwhaleAISenv21.rda')
saveRDS(env22, 'data/GPSwhaleAISenv22.rda')
saveRDS(env23, 'data/GPSwhaleAISenv23.rda')
saveRDS(env07, 'data/GPSwhaleAISenv07.rda')
saveRDS(env08, 'data/GPSwhaleAISenv08.rda')
